---
title: "individual1"
author: "Luping"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Individual Work:** Luping Wang
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```

1.How are ratings distributed? Don’t forget to mention outliers, if there are any.
```{r}
##str(choco)
hist(choco$Rating)
boxplot(choco$Rating)

```

According to the histogram, it's a bell-shaped distrubution. Most of ratings fall within the range of 2.5 and 3.5. Accoding to the boxplot, there are several outliers.

2.Do ratings depend on the cacao percentage of a chocolate bar?
```{r}

plot(choco$Cocoa.Pct ~ choco$Rating,ylim=c(1,100),col="blue",pch=18, cex=1.5,xlab="Rating scale", ylab= "Cocoa Percentage", main= "Rating VS cacao percentage") 
```

According to the graphs generatded above, I think "ratings" is related to "cacao percentage of a chocolate bar".Higher Cocoa Percentage, the more the number of ratings.


3.What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)
```{r}
class(choco$Company.Location)
```
It's a factor. Character is letters and LETTERS which provide the 26 lower (and upper)
case letters.  Factor is A type vector contains a set of numeric codes with character-valued levels.
