---
title: "individual1"
author: "Luping"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.How are ratings distributed? Don’t forget to mention outliers, if there are any.
```{r}
##str(choco)
hist(choco$Rating)
##plot(choco$Rating)
```
It's a bell-shaped distrubution. Most of ratings fall within the range of 2.5 and 3.5. 

2.Do ratings depend on the cacao percentage of a chocolate bar?
```{r}
hist(choco$Cocoa.Pct)
```
According to the graphs generatded above, I think "ratings" is related to "cacao percentage of a chocolate bar".


3.What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)
```{r}
class(choco$Company.Location)
```
It's a factor. Character is letters and LETTERS which provide the 26 lower (and upper)
case letters.  Factor is A type vector contains a set of numeric codes with character-valued levels.
