---
title: "Lab 2"
author: "Brenna Walters"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco = read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```

#Questions

1. Distribution of Ratings
```{r}
hist(choco$Rating, main="Distribution of Rating",xlab="Rating")
```
This distribution is unimodal, slightly left skewed, and has one upper outlier.\

2. Does rating depend on cocao percentage?
```{r}
library(ggplot2)
qplot(Cocoa.Pct, Rating, data=choco, main = "Cocoa % vs Rating")
```
\
From this plot, it looks like a cocao percentage in the middle to upper range (about 55% to ~ 90%) has the largest number of ratings. The 0% to %40 range has no ratings, so we see that the number of ratings does depend of cocao percentage.\

3. What class is the variable representing company locations? How is this different from a 'character' variable?\
```{r}
class(choco$Company.Location)
```
The difference is that a character can be any string, while a factor is actually a value stored with a label. For that reason, they should not be treated the same when they're being used.\

