---
title: "team"
author: "Luping"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1 . Run the following code line by line to figure out what it’s doing. Then next to each line of code, write a comment explaining its purpose and function, including the use of any specific arguments. Comments in R are proceeded by a #, so that R knows not to run anything after the hashtag.

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)

plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 

recent_rating = choco[choco$Review.Date>2011,]# It gives me the rows where the review date is after the year 2011.


unique(recent_rating$Company.Location) # It gives me unique companies' locations in the recent_rating data set. NOTICE: how many countries are listed but how many levels are there? 54 countries are listed, there are 61 levels.

recent_rating$Company.Location = droplevels(recent_rating$Company.Location) # drop unused levels from a factor. Now, the level of recent_rating is 54.

head(recent_rating) # It returns the top 6 rows of recent_rating where review data>2011 

cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location)
cross_table 
#create a table named cross_table: rows are review dates from recent_rating & columns are company.location from recent_rating. We want to know how many review dates occur at different company loactions from year 2012-2017. 

which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0)# return the Company.Location indexes where the review date in 1st,2nd,3rd,4th,5th rows are not 0.

france_recent = subset(recent_rating,Company.Location =='France')#create a dataset named france_recent, it returns the recent_rating where the location is France
uk_recent = subset(recent_rating,Company.Location =='U.K.')#create a dataset named uk_recent, it returns the recent_rating where the location is U.K.
germany_recent = subset(recent_rating,Company.Location=='Germany')#create a dataset named germany_recent, it returns the recent_rating where the location is Germany.


par(mfrow=c(2,2)) ## With the par( ) function, you can include the option mfrow=c(nrows, ncols) to create a matrix of nrows x ncols plots that are filled in by row. mfcol=c(nrows, ncols) fills in the matrix by columns. Set up the layout(it allows to generate 4 graphs in one page)
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green')
# Identify the object color 1: if the rating is larger than the median rating in france_recent dataset,change the color into blue. if not, change it into green.
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") 
#creates a plot with Review_Date (from france_recent subset) on x-axis and Cocoa Percentage from (france_recent subset) on y-axis. The title for the graph is "France".The color of points is defined by color1. The symbol of points is set to be a filled diamond (pch=18) and the size of the points is adjusted to be larger (cex=1.5). 

legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18)
# add a legend to the plot. Display the bottom right corner of a rectangular data set(bottomright). Create 2 legends which are "High Rating" and "Low Rating"(legend=c('High Rating', 'Low Rating')). The color of "High Rating" is "blue" and The color of "Low Rating" is "green"(col=c('blue','green')). The plotting symbols appearing in the legend is filled diamond(pch=18).

color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red')
# Identify the object color 2: if the rating is larger than the median rating in uk_recent dataset,change the color into purple. if not, change it into red.
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK")
# creates a plot with Review_Date (from uk_recent subset) on x-axis and Cocoa Percentage from (uk_recent subset) on y-axis. The title for the graph is "UK" (main= "UK").Set the range of y axis(Cocoa Percentage)from 50-90 (ylim=c(50,90)). The color of points is defined by color2(col=color2). The symbol of points is set to be a filled diamond (pch=18) and the size of the points is adjusted to be larger (cex=1.5). 

legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18)
# add a legend to the plot. Display the bottom right corner of a rectangular data set(bottomright). Create 2 legends which are "High Rating" and "Low Rating"(legend=c('High Rating', 'Low Rating')). The color of "High Rating" is "purple" and The color of "Low Rating" is "red"(col=c('purple','red')). The plotting symbols appearing in the legend is filled diamond(pch=18).

color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow')
# Identify the object color 3: if the rating is larger than the median rating in uk_recent dataset,change the color into orange. if not, change it into yellow.
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") 
#creates a plot with Review_Date (from germany_recent subset) on x-axis and Cocoa Percentage from (germany_recent subset) on y-axis. The title for the graph is "Germany" (main= "Germany").Set the range of y axis(Cocoa Percentage)from 50-90 (ylim=c(50,90)). The color of points is defined by color3(col=color3). The symbol of points is set to be a filled diamond (pch=18) and the size of the points is adjusted to be larger (cex=1.5). 
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18)
#add a legend to the plot. Display the bottom right corner of a rectangular data set(bottomright). Create 2 legends which are "High Rating" and "Low Rating"(legend=c('High Rating', 'Low Rating')). The color of "High Rating" is "orange" and The color of "Low Rating" is "yellow"(col=c('orange','yellow')). The plotting symbols appearing in the legend is filled diamond(pch=18).
```
2 . Click Zoom on the Rstudio window (under Plots) to see the plot more clearly. How do you think the plot produced from the code above can be improved? Recommend at least one possible improvement.

The legends are too big for the plots.

3 . How does the number of ratings (not the actual value of the rating) depend on the year? Use graphics to answer this question.
```{r}
Rating_Year<-table(choco$Rating,choco$Review.Date)
SumRating<-colSums(Rating_Year) #vector
barplot(SumRating)               
```
\
From this graph, we see that the number of ratings increased overall, reached a maximum in 2015, then decreased in 2016 and 2017.\

4 . How do ratings compare across different company locations? Focus on the three locations with the most ratings. Hint: the function sort() might come in handy here.
```{r}
newTable<-table(choco$Rating,choco$Company.Location)
Ratings_Location<-colSums(newTable)#Ratings_Location is table, colSums adds all values in each column.
sort(Ratings_Location,decreasing = TRUE)# top 3 Locations are U.S.A., France and Canada

con<-cbind(newTable[,"U.S.A."],newTable[,"France"],newTable[,"Canada"]) #vector
con<-data.frame(con)

ra<-sort(unique(choco$Rating),decreasing=FALSE) #sort the ratings from smallest to largest. Gonna be x axis
par(mfrow=c(2,2))
plot(ra,con$X1,pch=18,col='blue',xlab="rating",ylab='USA')
plot(ra,con$X2,pch=18,col='green',xlab="rating",ylab='France')
plot(ra,con$X3,pch=18,col='red',xlab="rating",ylab='Canada')
```

5 . Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.\
***Ideas:*** We could look at what countries use a higher percent of cacoa, which countries use what type of bean, or how the origin of the bean affects the rating


6 . Bonus points (optional): Answer the question from the dataset.
